no interaction

### 2022-08-29 graphs_newt_snakes/Heritability.Rmd
I am writing and making my markdown more readable

@@

her_tall <- list.files(path="~/Desktop/no_hair", pattern="_lit_", full.names=TRUE, recursive=FALSE)
her_tall_cor_files <- list.files(path="~/Desktop/no_hair", pattern="_cor_", full.names=TRUE, recursive=FALSE)
her_her_grid_tall_files <- list.files(path="~/Desktop/no_hair", pattern="_grid_", full.names=TRUE, recursive=FALSE)

her_tall_tall_file<- data.frame()
her_cor_tall_file<- data.frame()
her_her_grid_tall_file<-data.frame()
name_list<-c()
cor_name_list<-c()
grid_name_list<-c()
for(i in seq(1, length(her_tall), 1)){
  print(i)
  #sim

  her_temp_file <- read.csv(her_tall[i], header = TRUE)
  her_temp_file$rep <- unlist(str_split(unlist(str_split(her_tall[i],"rep_"))[3], "_"))[1]
  her_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_rate_"))[2], "_"))[1]
  her_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_rate_"))[2], "_"))[1]
  her_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  her_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  name_list<-c(paste0(her_temp_file$snake_mu_rate[1], her_temp_file$newt_mu_rate[1], her_temp_file$snake_mu_effect_sd[1], her_temp_file$newt_mu_effect_sd[1]),name_list)
  her_temp_file$sim <- LETTERS[length(unique(name_list))]
  her_tall_tall_file <- rbind(her_tall_tall_file, her_temp_file)
  print(her_temp_file$sim[1])

  cor_temp_file <- read.csv(her_tall_cor_files[i], header = TRUE)
  cor_temp_file$sim <-
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(her_tall_cor_files[i],"rep_"))[3], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
  her_cor_tall_file <- rbind(her_cor_tall_file, cor_temp_file)
  print(cor_temp_file$sim[1])

  her_grid_temp_file <- read.csv(her_her_grid_tall_files[i], header = TRUE)
  her_grid_temp_file$sim <-
  her_grid_temp_file$rep <-unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"rep_"))[3], "_"))[1]
  her_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
  her_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
  her_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  her_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(her_her_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  grid_name_list<-c(paste0(her_grid_temp_file$snake_mu_rate[1], her_grid_temp_file$newt_mu_rate[1], her_grid_temp_file$snake_mu_effect_sd[1], her_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
  her_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
  her_her_grid_tall_file <- rbind(her_her_grid_tall_file, her_grid_temp_file)
   print(her_grid_temp_file$sim[1])

her_tall_tall_file$dif <- her_tall_tall_file$Snake_mean_Pheno-her_tall_tall_file$Newt_mean_Pheno

@@

her_her_grid_tall_file$snake_newt_rep <- paste0("Snake_",her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd, "_Newt_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd, "_", her_her_grid_tall_file$rep)

@@

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=GA3_tall_tall_file
#cfile=GA3_cor_tall_file 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

@@

file_name= "Snake_1.0e-11_5.0_Newt_1.0e-11_5.0_0"
#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0

>>>>

```{bash, data file gathering}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=no_hair
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

@@

folder="no_hair"
filelocation=paste0("~/Desktop/",folder)

her_tall_tall_file<- read.csv(paste0(filelocation, "/all_lit.txt") , header = TRUE)

@@

her_tall_tall_file$sim=LETTERS[factor(her_tall_tall_file$group)]
her_tall_tall_file$dif <- her_tall_tall_file$Snake_mean_Pheno-her_tall_tall_file$Newt_mean_Pheno

her_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
her_cor_tall_file$group <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd)
her_cor_tall_file$sim=LETTERS[factor(her_cor_tall_file$group)]

her_her_grid_tall_file<-read.csv(paste0(filelocation,"/all_grid.txt") , header = TRUE)
her_her_grid_tall_file$group <- paste0(her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd,"_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd)
her_her_grid_tall_file$group_rep <- paste0(her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd,"_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd, "_", her_her_grid_tall_file$rep)

her_her_grid_tall_file$sim=LETTERS[factor(her_her_grid_tall_file$group)]
her_her_grid_tall_file$snake_newt_rep <- paste0("Snake_",her_her_grid_tall_file$snake_mu_rate, "_", her_her_grid_tall_file$snake_mu_effect_sd, "_Newt_",her_her_grid_tall_file$newt_mu_rate, "_", her_her_grid_tall_file$newt_mu_effect_sd, "_", her_her_grid_tall_file$rep)

@@

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=GA3_tall_tall_file
#cfile=GA3_cor_tall_file 
 # pattern="1e-10_0.05_1e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

@@

file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
#Snake_1e-09_0.05_Newt_1e-09_0.05_2
#Snake_1e-08_0.005_Newt_1e-11_0.158_0

### 2022-08-29 graphs_newt_snakes/no_interact.Rmd
I am writing and making my markdown more readable

In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-interitable trait. I expect to see no spatial phenotype correlation

@@

```{r, data gatintering}

@@

inter_tall <- list.files(path="~/Desktop/no_interaction", pattern="_lit_", full.names=TRUE, recursive=FALSE)
inter_tall_cor_files <- list.files(path="~/Desktop/no_interaction", pattern="_cor_", full.names=TRUE, recursive=FALSE)
inter_inter_grid_tall_files <- list.files(path="~/Desktop/no_interaction", pattern="_grid_", full.names=TRUE, recursive=FALSE)

inter_tall_tall_file<- data.frame()
inter_cor_tall_file<- data.frame()
inter_inter_grid_tall_file<-data.frame()
name_list<-c()
cor_name_list<-c()
grid_name_list<-c()
for(i in seq(1, length(inter_tall), 1)){
  print(i)
  #sim

  inter_temp_file <- read.csv(inter_tall[i], header = TRUE)
  inter_temp_file$rep <- unlist(str_split(unlist(str_split(inter_tall[i],"rep_"))[2], "_"))[1]
  inter_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_tall[i],"snake_mu_rate_"))[2], "_"))[1]
  inter_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_tall[i],"newt_mu_rate_"))[2], "_"))[1]
  inter_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  inter_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  name_list<-c(paste0(inter_temp_file$snake_mu_rate[1], inter_temp_file$newt_mu_rate[1], inter_temp_file$snake_mu_effect_sd[1], inter_temp_file$newt_mu_effect_sd[1]),name_list)
  inter_temp_file$sim <- LETTERS[length(unique(name_list))]
  inter_tall_tall_file <- rbind(inter_tall_tall_file, inter_temp_file)
  print(inter_temp_file$sim[1])

  cor_temp_file <- read.csv(inter_tall_cor_files[i], header = TRUE)
  cor_temp_file$sim <-
  cor_temp_file$rep <-unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"rep_"))[2], "_"))[1]
  cor_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"snake_mu_rate_"))[2], "_"))[1]
  cor_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"newt_mu_rate_"))[2], "_"))[1]
  cor_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  cor_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_tall_cor_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  cor_name_list<-c(paste0(cor_temp_file$snake_mu_rate[1], cor_temp_file$newt_mu_rate[1], cor_temp_file$snake_mu_effect_sd[1], cor_temp_file$newt_mu_effect_sd[1]),cor_name_list)
  cor_temp_file$sim <- LETTERS[length(unique(cor_name_list))]
  inter_cor_tall_file <- rbind(inter_cor_tall_file, cor_temp_file)
  print(cor_temp_file$sim[1])

  inter_grid_temp_file <- read.csv(inter_inter_grid_tall_files[i], header = TRUE)
  inter_grid_temp_file$sim <-
  inter_grid_temp_file$rep <-unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"rep_"))[2], "_"))[1]
  inter_grid_temp_file$snake_mu_rate <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"snake_mu_rate_"))[2], "_"))[1]
  inter_grid_temp_file$newt_mu_rate <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"newt_mu_rate_"))[2], "_"))[1]
  inter_grid_temp_file$snake_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"snake_mu_effect_sd_"))[2], "_"))[1]
  inter_grid_temp_file$newt_mu_effect_sd <- unlist(str_split(unlist(str_split(inter_inter_grid_tall_files[i],"newt_mu_effect_sd_"))[2], "_"))[1]
  grid_name_list<-c(paste0(inter_grid_temp_file$snake_mu_rate[1], inter_grid_temp_file$newt_mu_rate[1], inter_grid_temp_file$snake_mu_effect_sd[1], inter_grid_temp_file$newt_mu_effect_sd[1]),grid_name_list)
  inter_grid_temp_file$sim <- LETTERS[length(unique(grid_name_list))]
  inter_inter_grid_tall_file <- rbind(inter_inter_grid_tall_file, inter_grid_temp_file)
   print(inter_grid_temp_file$sim[1])

inter_tall_tall_file$dif <- inter_tall_tall_file$Snake_mean_Pheno-inter_tall_tall_file$Newt_mean_Pheno

@@

inter_inter_grid_tall_file$snake_newt_rep <- paste0("Snake_",inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd, "_Newt_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd, "_", inter_inter_grid_tall_file$rep)

@@

file_name= "Snake_1.0e-11_5.0_Newt_1.0e-11_5.0_0"
#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0

@@

file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0

>>>>

In this experiment I am observing a co-evolving population (survival is determined by a random draw) with a non-interactible trait. I expect to see no spatial phenotype correlation

@@

```{bash, data file gathering}
#!/usr/bin/env bash

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=no_interaction
thefolder=${thepath}${foldername}/*

add_in_column=",rep,snake_mu_rate,snake_mu_effect_sd,newt_mu_rate,newt_mu_effect_sd"

cor_head_file=$(find ${thepath}${foldername} -name "*_cor_*" | head -n 1)
cor_head=$(head -n 1 "${cor_head_file}")

grid_head_file=$(find ${thepath}${foldername} -name "*_grid_*" | head -n 1)
grid_head=$(head -n 1 "${grid_head_file}")

lit_head_file=$(find ${thepath}${foldername} -name "*_lit_*" | head -n 1)
lit_head=$(head -n 1 "${lit_head_file}")

#test -f /Users/victoria/Desktop/bash_test/all_lit.txt && echo "all lit file exists."
#test -f /Users/victoria/Desktop/bash_test/all_grid.txt && echo "all grid file exists."
#test -f /Users/victoria/Desktop/bash_test/all_cor.txt && echo "all cor file exists."

if [[ -f ${thepath}${foldername}/all_lit.txt ]] && [[ -f ${thepath}${foldername}/all_grid.txt ]] && [[ -f ${thepath}${foldername}/all_cor.txt ]]
then
  echo "All cor, lit, and grid files exist!"
  echo "This program will now end!"
  exit 0
fi

#creating the files
echo ${lit_head}${add_in_column} > ${thepath}${foldername}/all_lit.txt
echo ${grid_head}${add_in_column} > ${thepath}${foldername}/all_grid.txt
echo ${cor_head}${add_in_column} > ${thepath}${foldername}/all_cor.txt

for filename in $thefolder*.text;
  do 
#getting the variables 
my_type=$(echo ${filename} |sed 's/.*GA205_//; s/_.*//')
snake_mu_rate=$(echo ${filename} |sed 's/.*snake_mu_rate_//; s/_.*//')
snake_mu_effect_sd=$(echo ${filename} |sed 's/.*snake_mu_effect_sd_//; s/_.*//')
newt_mu_rate=$(echo ${filename} |sed 's/.*newt_mu_rate_//; s/_.*//')
newt_mu_effect_sd=$(echo ${filename} |sed 's/.*newt_mu_effect_sd_//; s/_.*//')
rep=$(echo ${filename} | sed "s/.*rep_//; s/_.*//")
#echo ${newt_mu_rate}	
# echo $my_type
# echo $my_other_type
# these new columns adding them to the data
sed -i '' -e 's/$/,'${rep}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${snake_mu_effect_sd}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_rate}'/' $filename
sed -i '' -e 's/$/,'${newt_mu_effect_sd}'/' $filename
#infile >outfile
if [[ $my_type == "lit" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_lit.txt
fi

if [[ $my_type == "grid" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_grid.txt
fi

if [[ $my_type == "cor" ]]
then
    tail -n +2 -q $filename >> ${thepath}${foldername}/all_cor.txt
fi

done

```{r, data gathering}

@@

folder="no_interaction"
filelocation=paste0("~/Desktop/",folder)

inter_tall_tall_file<- read.csv(paste0(filelocation, "/all_lit.txt") , header = TRUE)

@@

inter_tall_tall_file$sim=LETTERS[factor(inter_tall_tall_file$group)]
inter_tall_tall_file$dif <- inter_tall_tall_file$Snake_mean_Pheno-inter_tall_tall_file$Newt_mean_Pheno

inter_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
inter_cor_tall_file$group_rep <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd, "_", inter_cor_tall_file$rep)
inter_cor_tall_file$group <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd)
inter_cor_tall_file$sim=LETTERS[factor(inter_cor_tall_file$group)]

inter_inter_grid_tall_file<-read.csv(paste0(filelocation,"/all_grid.txt") , header = TRUE)
inter_inter_grid_tall_file$group <- paste0(inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd,"_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd)
inter_inter_grid_tall_file$group_rep <- paste0(inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd,"_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd, "_", inter_inter_grid_tall_file$rep)

inter_inter_grid_tall_file$sim=LETTERS[factor(inter_inter_grid_tall_file$group)]
inter_inter_grid_tall_file$snake_newt_rep <- paste0("Snake_",inter_inter_grid_tall_file$snake_mu_rate, "_", inter_inter_grid_tall_file$snake_mu_effect_sd, "_Newt_",inter_inter_grid_tall_file$newt_mu_rate, "_", inter_inter_grid_tall_file$newt_mu_effect_sd, "_", inter_inter_grid_tall_file$rep)

@@

file_name= "Snake_1e-11_5_Newt_1e-11_5_0"
#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0

@@

file_name= "Snake_1e-08_0.005_Newt_1e-08_0.005_3"
#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0
